Revised Interoceptive Accuracy Scale (IAS-R)

### 2024-02-20 analysis/analysis.qmd
update stats

# Campos (2022) - Study 1 (https://osf.io/j6ef3)
df3 <- haven::read_sav("../data/Campos2022/Dataset_Test.sav") |> 
  mutate_all(as.numeric) |> 
  mutate(Gender = as.character(ifelse(Sex == 1, "Male", ifelse(Sex == 0, "Female", "Other")))) |> 
  rename(Heart=IAS1, Hungry=IAS2, Breathing=IAS3, Thirsty=IAS4,
         Urinate=IAS5, Defecate=IAS6, Taste=IAS7, Vomit=IAS8, Sneeze=IAS9,
         Cough=IAS10, Temp=IAS11, Sex_arousal=IAS12, Wind=IAS13, Burp=IAS14,
         Muscles=IAS15, Bruise=IAS16, Pain=IAS17, Blood_Sugar=IAS18,
         Affective_touch=IAS19, Tickle=IAS20, Itch=IAS21)

# https://osf.io/3eztd
df4 <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |> 
  mutate(Gender = as.character(ifelse(sex_dummy == 1, "Male", ifelse(sex_dummy == 0, "Female", "Other")))) |> 
  rename(Age=age, 
         Heart=Heart, Hungry=HUNGR, Breathing=BREAT, Thirsty=Thirs,
         Urinate=URINA, Defecate=Defec, Taste=TASTE, Vomit=VOMIT, Sneeze=Sneez,
         Cough=COUGH, Temp=TEMPE, Sex_arousal=SEXAR, Wind=WIND, Burp=Burp,
         Muscles=MUSCL, Bruise=Bruis, Pain=PAIN, Blood_Sugar=BloSu,
         Affective_touch=Touch, Itch=ITCH)  # No tickle because same Chinese character

# https://osf.io/3eztd
df5 <- haven::read_sav("../data/Lin2023/Study 2.sav") |> 
  mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |> 
  rename(Heart=Heart, Hungry=HUNGR, Breathing=BREAT, Thirsty=Thirs,
         Urinate=URINA, Defecate=Defec, Taste=TASTE, Vomit=VOMIT, Sneeze=Sneez,
         Cough=COUGH, Temp=TEMPE, Sex_arousal=SEXAR, Wind=WIND, Burp=Burp,
         Muscles=MUSCL, Bruise=Bruis, Pain=PAIN, Blood_Sugar=BloSu,
         Affective_touch=Touch, Itch=ITCH)  # No tickle because same Chinese character

df6 <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
  rename(Heart=IAS_1, Hungry=IAS_2, Breathing=IAS_3, Thirsty=IAS_4, 
         Urinate=IAS_5, Defecate=IAS_6, Taste=IAS_7, Vomit=IAS_8, Sneeze=IAS_9, 
         Cough=IAS_10, Temp=IAS_11, Sex_arousal=IAS_12, Wind=IAS_13, Burp=IAS_14,
         Muscles=IAS_15, Bruise=IAS_16, Pain=IAS_17, Blood_Sugar=IAS_18,
         Affective_touch=IAS_19, Tickle=IAS_20, Itch=IAS_21)

df7 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(Gender=Sex, Heart=Item_IAS_Interoception_1, Hungry=Item_IAS_Interoception_2, 
         Breathing=Item_IAS_Interoception_3, Thirsty=Item_IAS_Interoception_4, 
         Temp=Item_IAS_Interoception_5, Sex_arousal=Item_IAS_Interoception_6,
         Urinate=Item_IAS_Elimination_1, Defecate=Item_IAS_Elimination_2,
         Vomit=Item_IAS_Elimination_3, Wind=Item_IAS_Expulsion_1, 
         Burp=Item_IAS_Expulsion_2, Sneeze=Item_IAS_Expulsion_3,
         Muscles=Item_IAS_Nociception_1, Bruise=Item_IAS_Nociception_2,
         Pain=Item_IAS_Nociception_3, Affective_touch=Item_IAS_Skin_1, 
         Tickle=Item_IAS_Skin_2, Itch=Item_IAS_Skin_3) |>
  filter(!is.na(Urinate))
```

@@

```{r}
vars <- c("Heart", "Hungry", "Breathing", "Thirsty", "Urinate", "Defecate", "Taste", "Vomit", "Sneeze", "Cough", "Temp",
          "Sex_arousal", "Wind", "Burp", "Muscles", "Bruise", "Pain", "Blood_Sugar", "Affective_touch", "Tickle", "Itch")

dens1 <- estimate_density(select(df1, all_of(vars)), method="kernSmooth") |> 
  mutate(Sample = "Sample 1")
dens2 <- estimate_density(select(df2, all_of(vars)), method="kernSmooth") |> 
  mutate(Sample = "Sample 2")
dens3 <- estimate_density(select(df3, all_of(vars)), method="kernSmooth") |> 
  mutate(Sample = "Sample 3")
dens4 <- estimate_density(select(df4, all_of(setdiff(vars, "Tickle"))), method="kernSmooth") |> 
  mutate(Sample = "Sample 4")
dens5 <- estimate_density(select(df5, all_of(setdiff(vars, "Tickle"))), method="kernSmooth") |> 
  mutate(Sample = "Sample 5")
dens6 <- estimate_density(select(df6, all_of(vars)), method="kernSmooth") |> 
  mutate(Sample = "Sample 6")
dens7 <- estimate_density(select(df7, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method="kernSmooth") |> 
  mutate(Sample = "Sample 7")

rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Distribution of Responses", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free", nrow=4)
```

```{r}
data1 <- normalize(select(df1, all_of(dens1$Parameter)), range=c(1, 5))
data2 <- normalize(select(df2, all_of(dens2$Parameter)), range=c(1, 5))
data3 <- normalize(select(df3, all_of(dens3$Parameter)), range=c(1, 5))
data4 <- normalize(select(df4, all_of(dens4$Parameter)), range=c(1, 5))
data5 <- normalize(select(df5, all_of(dens5$Parameter)), range=c(1, 5))
data6 <- select(df6, all_of(dens6$Parameter))
data7 <- select(df7, all_of(dens7$Parameter))

data_all <- rbind(data1, data2, data3, 
                  mutate(data4, Tickle=NA), mutate(data5, Tickle=NA), 
                  data6, mutate(data7, Taste=NA, Cough=NA, Blood_Sugar=NA)) 
```

@@

```{r}
make_correlation <- function(df) {
  correlation::correlation(df, redundant=TRUE) |> 
    correlation::cor_sort() |> 
    correlation::cor_lower() |> 
    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only=TRUE))) |>
    mutate(Parameter2 = fct_rev(Parameter2)) |>
    ggplot(aes(x=Parameter1, y=Parameter2)) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = val), size = 3) +
    labs(title = "Correlation Matrix") +
    scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks=FALSE)) +
    theme_minimal() +
    theme(legend.title = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_text(angle = 45, hjust = 1))
}

@@

### EGA

See https://r-ega.net/articles/ega.html for details.

@@

@@

#### Item Stability

@@

plots <- list()
for(model in c("glasso", "TMFG")) {
  for(algo in c("walktrap", "louvain")) {
    for(type in c("ega", "ega.fit")) {  # "hierega"
      print(type)
      ega <- EGAnet::bootEGA(
        data = data_all,
        seed=123,
        model=model,
        algorithm=algo,
        EGA.type=type,
        type="resampling",
        plot.itemStability=FALSE,
        verbose=FALSE)
      plots[[length(plots) + 1]] <- plot(ega) + 
        labs(title = paste0(model, " (", algo, ") - ", type))
      }
    }
}

length(plots)
patchwork::wrap_plots(plots, nrow = 4)
```

<!-- ::: {.panel-tabset} -->

<!-- ##### glasso model (Walktrap) -->

<!-- ```{r ega1} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
<!--   ega <- EGAnet::bootEGA( -->
<!--     data = d, -->
<!--     seed=123, -->
<!--     model="glasso", -->
<!--     algorithm="walktrap", -->
<!--     type="resampling", -->
<!--     EGA.type="ega", -->
<!--     plot.itemStability=FALSE,  -->
<!--     verbose=FALSE) -->
<!--   plots[[length(plots) + 1]] <- plot(ega) -->
<!-- } -->

<!-- EGAnet::dimensionStability(ega) -->
<!-- (plots[[1]] + labs(title = "Sample 1") + -->
<!--   plots[[2]] + labs(title = "Sample 2")) / -->
<!--   (plots[[3]] + labs(title = "Sample 3") + -->
<!--   plots[[4]] + labs(title = "Sample 4")) / -->
<!--   (plots[[5]] + labs(title = "Sample 5") + -->
<!--   plots[[6]] + labs(title = "Sample 6")) -->
<!-- ``` -->

<!-- ##### glasso model (Louvain) -->

<!-- ```{r ega2} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
<!--   ega <- EGAnet::bootEGA( -->
<!--     data = d, -->
<!--     seed=123, -->
<!--     model="glasso", -->
<!--     algorithm="louvain", -->
<!--     plot.itemStability=FALSE) -->
<!--   plots[[length(plots) + 1]] <- plot(ega) -->
<!-- } -->

<!-- (plots[[1]] + labs(title = "Sample 1") + -->
<!--   plots[[2]] + labs(title = "Sample 2")) / -->
<!--   (plots[[3]] + labs(title = "Sample 3") + -->
<!--   plots[[4]] + labs(title = "Sample 4")) / -->
<!--   (plots[[5]] + labs(title = "Sample 5") + -->
<!--   plots[[6]] + labs(title = "Sample 6")) -->
<!-- ``` -->

<!-- ##### TMFG model (Walktrap) -->

<!-- ```{r ega3} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
<!--   ega <- EGAnet::bootEGA( -->
<!--     data = d, -->
<!--     seed=123, -->
<!--     model="TMFG", -->
<!--     algorithm="walktrap", -->
<!--     plot.itemStability=FALSE) -->
<!--   plots[[length(plots) + 1]] <- plot(ega) -->
<!-- } -->

<!-- (plots[[1]] + labs(title = "Sample 1") + -->
<!--   plots[[2]] + labs(title = "Sample 2")) / -->
<!--   (plots[[3]] + labs(title = "Sample 3") + -->
<!--   plots[[4]] + labs(title = "Sample 4")) / -->
<!--   (plots[[5]] + labs(title = "Sample 5") + -->
<!--   plots[[6]] + labs(title = "Sample 6")) -->
<!-- ``` -->

<!-- ##### TMFG model (Louvain) -->

<!-- ```{r ega4} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(d in list(data1, data2, data3, data4, data5, data6)) { -->
<!--   ega <- EGAnet::bootEGA( -->
<!--     data = d, -->
<!--     seed=123, -->
<!--     model="TMFG", -->
<!--     algorithm="louvain", -->
<!--     plot.itemStability=FALSE) -->
<!--   plots[[length(plots) + 1]] <- plot(ega) -->
<!-- } -->

<!-- (plots[[1]] + labs(title = "Sample 1") + -->
<!--   plots[[2]] + labs(title = "Sample 2")) / -->
<!--   (plots[[3]] + labs(title = "Sample 3") + -->
<!--   plots[[4]] + labs(title = "Sample 4")) / -->
<!--   (plots[[5]] + labs(title = "Sample 5") + -->
<!--   plots[[6]] + labs(title = "Sample 6")) -->
<!-- ``` -->

<!-- ##### All data -->

<!-- ```{r ega1} -->
<!-- #| fig-height: 12 -->

<!-- plots <- list() -->
<!-- for(model in c("glasso", "TMFG")) { -->
<!--   for(algo in c("walktrap", "louvain")) { -->
<!--     ega <- EGAnet::bootEGA( -->
<!--       data = data_all, -->
<!--       seed=123, -->
<!--       model=model, -->
<!--       algorithm=algo, -->
<!--       plot.itemStability=FALSE) -->
<!--     plots[[length(plots) + 1]] <- plot(ega) +  -->
<!--       labs(title = paste0(model, " (", algo, ")")) -->
<!--   } -->
<!-- } -->

<!-- patchwork::wrap_plots(plots) -->
<!-- ``` -->

<!-- ::: -->

### Exploratory Factor Analysis (EFA)

@@

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4, 5 ), ], row.names = FALSE)
```

@@

#### EFA Models

@@

efa5 <- parameters::factor_analysis(data_all, n=5, rotation = "oblimin", sort = TRUE)
plot(efa5)

@@

efa4 <- parameters::factor_analysis(data2, n=4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data3, n=4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa5 <- parameters::factor_analysis(data4, n=5, rotation = "oblimin", sort = TRUE)
plot(efa5)

@@

efa5 <- parameters::factor_analysis(data5, n=5, rotation = "oblimin", sort = TRUE)
plot(efa5)

@@

efa4 <- parameters::factor_analysis(data5, n=4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

### Model Construction

@@

```{r}
m1 <- "
Interoception =~ Hungry + Thirsty + Urinate + Defecate + Itch + Bruise + Muscles + Pain + Breathing + Heart + Cough + Sneeze + Wind + Burp
"

m7 <- "
# ----
Sustenance =~ Hungry + Thirsty
Elimination =~ Urinate + Defecate
Skin =~ Itch + Bruise
Nociception =~ Muscles + Pain
Affect =~ Breathing + Heart
# ----
Expulsion =~ Cough + Sneeze + Wind + Burp

# --- 
# Ambiguous: Temp + Vomit + Affective_touch + Sex_arousal + Taste
# Discard: Tickle + Blood_Sugar
"

m8 <- "
# ----
Sustenance =~ Hungry + Thirsty
Elimination =~ Urinate + Defecate
Skin =~ Itch + Bruise
Nociception =~ Muscles + Pain
Affect =~ Breathing + Heart
# ----
Expulsion_Sudden =~ Cough + Sneeze 
Expulsion_Gastric =~ Wind + Burp
" 
# Ambiguous: Temp + Vomit + Affective_touch + Sex_arousal + Taste
# Discard: Tickle + Blood_Sugar

m1_all <- lavaan::cfa(m1, data = data_all)
m7_all <- lavaan::cfa(m7, data = data_all)
m8_all <- lavaan::cfa(m8, data = data_all)

anova(m1_all, m7_all, m8_all) |> 
  parameters::parameters() |> 
  display()
```

@@

```{r}
m8h1 <- paste0(m8, "
              Interoception =~ Sustenance + Elimination + Skin + Nociception + Affect + Expulsion_Sudden + Expulsion_Gastric
              ")

m8h3 <- paste0(m8, "
              Valenced =~ Nociception + Affect + Skin
              Expulsion =~ Expulsion_Sudden + Expulsion_Gastric 
              Homeostasis =~ Sustenance + Elimination
              ")

m8h1_all <- lavaan::cfa(m8h1, data = data_all)
m8h3_all <- lavaan::cfa(m8h3, data = data_all)
anova(m8_all, m8h1_all, m8h3_all) |> 
  parameters::parameters() |> 
  display()
```

>>>>

# Campos (2022) - Study 1 (https://osf.io/j6ef3)
df3 <- haven::read_sav("../data/Campos2022/Dataset_Test.sav") |>
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(Sex == 1, "Male", ifelse(Sex == 0, "Female", "Other")))) |>
  rename(
    Heart = IAS1, Hungry = IAS2, Breathing = IAS3, Thirsty = IAS4,
    Urinate = IAS5, Defecate = IAS6, Taste = IAS7, Vomit = IAS8, Sneeze = IAS9,
    Cough = IAS10, Temp = IAS11, Sex_arousal = IAS12, Wind = IAS13, Burp = IAS14,
    Muscles = IAS15, Bruise = IAS16, Pain = IAS17, Blood_Sugar = IAS18,
    Affective_touch = IAS19, Tickle = IAS20, Itch = IAS21
  )

# https://osf.io/3eztd
df4 <- haven::read_sav("../data/Lin2023/Study 1 & 3.sav") |>
  select(-sex) |> 
  mutate_all(as.numeric) |>
  mutate(Gender = as.character(ifelse(sex_dummy == 1, "Male", ifelse(sex_dummy == 0, "Female", "Other")))) |>
  rename(
    Age = age,
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH
  ) # No tickle because same Chinese character

# https://osf.io/3eztd
df5 <- haven::read_sav("../data/Lin2023/Study 2.sav") |>
  mutate(Gender = as.character(ifelse(Sex == "男", "Male", ifelse(Sex == "女", "Female", "Other")))) |>
  rename(
    Heart = Heart, Hungry = HUNGR, Breathing = BREAT, Thirsty = Thirs,
    Urinate = URINA, Defecate = Defec, Taste = TASTE, Vomit = VOMIT, Sneeze = Sneez,
    Cough = COUGH, Temp = TEMPE, Sex_arousal = SEXAR, Wind = WIND, Burp = Burp,
    Muscles = MUSCL, Bruise = Bruis, Pain = PAIN, Blood_Sugar = BloSu,
    Affective_touch = Touch, Itch = ITCH
  ) # No tickle because same Chinese character

df6 <- read.csv("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/study2/data/data.csv") |>
  rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  )

df7 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3
  ) |>
  filter(!is.na(Urinate))
```

@@

```{r}
vars <- c(
  "Heart", "Hungry", "Breathing", "Thirsty", "Urinate", "Defecate", "Taste", "Vomit", "Sneeze", "Cough", "Temp",
  "Sex_arousal", "Wind", "Burp", "Muscles", "Bruise", "Pain", "Blood_Sugar", "Affective_touch", "Tickle", "Itch"
)

dens1 <- estimate_density(select(df1, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1")
dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 2")
dens3 <- estimate_density(select(df3, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 3")
dens4 <- estimate_density(select(df4, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 4")
dens5 <- estimate_density(select(df5, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 5")
dens6 <- estimate_density(select(df6, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 6")
dens7 <- estimate_density(select(df7, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
  mutate(Sample = "Sample 7")

rbind(dens1, dens2, dens3, dens4, dens5, dens6, dens7) |>
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Distribution of Responses", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free", nrow = 4)
```

```{r}
data1 <- normalize(select(df1, all_of(dens1$Parameter)), range = c(1, 5))
data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
data4 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
data6 <- select(df6, all_of(dens6$Parameter))
data7 <- select(df7, all_of(dens7$Parameter))

data_all <- rbind(
  data1, data2, data3,
  mutate(data4, Tickle = NA), mutate(data5, Tickle = NA),
  data6, mutate(data7, Taste = NA, Cough = NA, Blood_Sugar = NA)
)
```

@@

```{r}
make_correlation <- function(df) {
  correlation::correlation(df, redundant = TRUE) |>
    correlation::cor_sort() |>
    correlation::cor_lower() |>
    mutate(val = paste0(insight::format_value(r), format_p(p, stars_only = TRUE))) |>
    mutate(Parameter2 = fct_rev(Parameter2)) |>
    ggplot(aes(x = Parameter1, y = Parameter2)) +
    geom_tile(aes(fill = r), color = "white") +
    geom_text(aes(label = val), size = 3) +
    labs(title = "Correlation Matrix") +
    scale_fill_metro_c(limit = c(0, 0.75), guide = guide_colourbar(ticks = FALSE)) +
    theme_minimal() +
    theme(
      legend.title = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1)
    )
}

@@

### Graph Analysis

Exploratory Graph Analysis (EGA) is a recently developed framework for psychometric assessment, that can be used to estimate the number of dimensions in questionnaire data using network estimation methods and community detection algorithms, and assess the stability of dimensions and items using bootstrapping.
See https://r-ega.net/articles/ega.html for details.

@@

Unique Variable Analysis (Christensen, Garrido, & Golino, 2023) uses the weighted topological overlap measure (Nowick et al., 2009) on an estimated network. Values greater than 0.25 are determined to have considerable local dependence (i.e., redundancy) that should be handled (variables with the highest maximum weighted topological overlap to all other variables (other than the one it is redundant with) should be removed).

@@

#### Networks

@@

make_egas <- function(data) {
  egas <- list()
  for (model in c("glasso", "TMFG")) {
    for (algo in c("walktrap", "louvain")) {
      for (type in c("ega", "ega.fit")) { # "hierega"
        if (type == "ega.fit" & algo == "louvain") next # Too slow
        egas[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
          data = data,
          seed = 123,
          model = model,
          algorithm = algo,
          EGA.type = type,
          type = "resampling",
          plot.itemStability = FALSE,
          verbose = FALSE
        )
      }
    }
  }

  p <- EGAnet::compare.EGA.plots(
    egas$glasso_walktrap_ega, egas$glasso_walktrap_ega.fit,
    egas$glasso_louvain_ega, egas$TMFG_louvain_ega,
    egas$TMFG_walktrap_ega, egas$TMFG_walktrap_ega.fit,
    labels = c(
      "glasso_walktrap_ega", "glasso_walktrap_ega.fit",
      "glasso_louvain_ega", "TMFG_louvain_ega",
      "TMFG_walktrap_ega", "TMFG_walktrap_ega.fit"
    ),
    rows = 3,
    plot.all = FALSE
  )$all
  list(egas = egas, p = p)
}

egas_all <- make_egas(data_all)
egas_all$p
```

```{r}
egas1 <- make_egas(data1)
egas1$p
```

```{r}
egas2 <- make_egas(data2)
egas2$p
```

```{r}
egas3 <- make_egas(data3)
egas3$p
```

```{r}
egas4 <- make_egas(data4)
egas4$p
```

```{r}
egas5 <- make_egas(data5)
egas5$p
```

```{r}
egas6 <- make_egas(data6)
egas6$p
```

```{r}
egas7 <- make_egas(data7)
egas7$p
```

#### Structure Stability

```{r}
#| fig-height: 20
#| fig-width: 12

patchwork::wrap_plots(lapply(egas_all$egas, plot), nrow = 3)
```

#### Scores

```{r}
ega <- egas_all$egas$glasso_louvain_ega$EGA
plot(ega)

ega_scores_1 <- EGAnet::net.scores(data1, ega)$scores$std.scores |>
  as.data.frame() |>
  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))

ega_scores_2 <- EGAnet::net.scores(data2, ega)$scores$std.scores |>
  as.data.frame() |>
  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))

ega_scores_3 <- EGAnet::net.scores(data3, ega)$scores$std.scores |>
  as.data.frame() |>
  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))

ega_scores_4 <- EGAnet::net.scores(data4, ega)$scores$std.scores |>
  as.data.frame() |>
  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))

ega_scores_5 <- EGAnet::net.scores(data5, ega)$scores$std.scores |>
  as.data.frame() |>
  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))

ega_scores_6 <- EGAnet::net.scores(data6, ega)$scores$std.scores |>
  as.data.frame() |>
  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))

ega_scores_7 <- EGAnet::net.scores(data7, ega)$scores$std.scores |>
  as.data.frame() |>
  setNames(c("EGA1", "EGA2", "EGA3", "EGA4"))
```

### Factor Analysis

@@

knitr::kable(as.data.frame(n)[n$n_Factors %in% c(1, 4, 5), ], row.names = FALSE)
```

@@

#### EFA

@@

efa5 <- parameters::factor_analysis(data_all, n = 5, rotation = "oblimin", sort = TRUE)
plot(efa5)

@@

efa4 <- parameters::factor_analysis(data2, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa4 <- parameters::factor_analysis(data3, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

efa5 <- parameters::factor_analysis(data4, n = 5, rotation = "oblimin", sort = TRUE)
plot(efa5)

@@

efa5 <- parameters::factor_analysis(data5, n = 5, rotation = "oblimin", sort = TRUE)
plot(efa5)

@@

efa4 <- parameters::factor_analysis(data6, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

efa4 <- parameters::factor_analysis(data7, n = 4, rotation = "oblimin", sort = TRUE)
plot(efa4)

@@

### CFA

@@

```{r}
# Ambiguous: Temp + Vomit + Affective_touch + Sex_arousal + Taste
# Discard: Tickle + Blood_Sugar

m1 <- "
Interoception =~ Hungry + Thirsty + Urinate + Defecate + Itch + Bruise + Muscles + Pain + Breathing + Heart + Cough + Sneeze + Wind + Burp
"

m4 <- "
Sustenance =~ Hungry + Thirsty + Urinate + Defecate + Muscles + Pain
Skin =~ Itch + Bruise
HeartBreathing =~ Breathing + Heart
Expulsion =~ Cough + Sneeze + Wind + Burp
"

m5 <- "
Sustenance =~ Hungry + Thirsty + Pain
UrinateDefecate =~ Urinate + Defecate
Skin =~ Itch + Bruise + Muscles
HeartBreathing =~ Breathing + Heart
Expulsion =~ Cough + Sneeze + Wind + Burp
"

m6 <- "
HungryThirsty =~ Hungry + Thirsty
UrinateDefecate =~ Urinate + Defecate
ItchBruise =~ Itch + Bruise
MusclesPain =~ Muscles + Pain
HeartBreathing =~ Breathing + Heart
Expulsion =~ Cough + Sneeze + Wind + Burp
"

m7 <- "
HungryThirsty =~ Hungry + Thirsty
UrinateDefecate =~ Urinate + Defecate
ItchBruise =~ Itch + Bruise
MusclesPain =~ Muscles + Pain
HeartBreathing =~ Breathing + Heart
CoughSneeze =~ Cough + Sneeze
WindBurp =~ Wind + Burp
"

m1_all <- lavaan::cfa(m1, data = data_all)
m4_all <- lavaan::cfa(m4, data = data_all)
m5_all <- lavaan::cfa(m5, data = data_all)
m6_all <- lavaan::cfa(m6, data = data_all)
m7_all <- lavaan::cfa(m7, data = data_all)

anova(m1_all, m4_all, m5_all, m6_all, m7_all) |>
  parameters::parameters() |>
  display()

parameters::parameters(m7_all, standardize=TRUE) |>
  display()
```

```{r}
anova(
  lavaan::cfa(m1, data = data1),
  lavaan::cfa(m4, data = data1),
  lavaan::cfa(m5, data = data1),
  lavaan::cfa(m6, data = data1),
  lavaan::cfa(m7, data = data1)
  ) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m1, data = data2),
  lavaan::cfa(m4, data = data2),
  lavaan::cfa(m5, data = data2),
  lavaan::cfa(m6, data = data2),
  lavaan::cfa(m7, data = data2)
  ) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m1, data = data3),
  lavaan::cfa(m4, data = data3),
  lavaan::cfa(m5, data = data3),
  lavaan::cfa(m6, data = data3),
  lavaan::cfa(m7, data = data3)
  ) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m1, data = data4),
  lavaan::cfa(m4, data = data4),
  lavaan::cfa(m5, data = data4),
  lavaan::cfa(m6, data = data4),
  lavaan::cfa(m7, data = data4)
  ) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m1, data = data5),
  lavaan::cfa(m4, data = data5),
  lavaan::cfa(m5, data = data5),
  lavaan::cfa(m6, data = data5),
  lavaan::cfa(m7, data = data5)
  ) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m1, data = data6),
  lavaan::cfa(m4, data = data6),
  lavaan::cfa(m5, data = data6),
  lavaan::cfa(m6, data = data6),
  lavaan::cfa(m7, data = data6)
  ) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(str_remove(m5, fixed("Cough + ")), data = data7),
  lavaan::cfa(str_remove(m1, fixed("Cough + ")), data = data7),
  lavaan::cfa(str_remove(m4, fixed("Cough + ")), data = data7),
  lavaan::cfa(str_remove(m6, fixed("Cough + ")), data = data7),
  lavaan::cfa(str_remove(m7, fixed("\nCoughSneeze =~ Cough + Sneeze")), data = data7)
  ) |>
  parameters::parameters() |>
  display()
```

@@

```{r}
m7h1 <- paste0(m7, "
              Interoception =~ HungryThirsty + UrinateDefecate + ItchBruise + MusclesPain + HeartBreathing + CoughSneeze + WindBurp
              ")

m7h3 <- paste0(m7, "
              Valenced =~ MusclesPain + HeartBreathing + ItchBruise
              Expulsion =~ CoughSneeze + WindBurp
              Homeostasis =~ HungryThirsty + UrinateDefecate
              ")

m7h1_all <- lavaan::cfa(m7h1, data = data_all)
m7h3_all <- lavaan::cfa(m7h3, data = data_all)
anova(m7_all, m7h1_all, m7h3_all) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m7, data = data1), 
  lavaan::cfa(m7h1, data = data1), 
  lavaan::cfa(m7h3, data = data1)) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m7, data = data2), 
  lavaan::cfa(m7h1, data = data2), 
  lavaan::cfa(m7h3, data = data2)) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m7, data = data3), 
  lavaan::cfa(m7h1, data = data3), 
  lavaan::cfa(m7h3, data = data3)) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m7, data = data4), 
  lavaan::cfa(m7h1, data = data4), 
  lavaan::cfa(m7h3, data = data4)) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m7, data = data5), 
  lavaan::cfa(m7h1, data = data5), 
  lavaan::cfa(m7h3, data = data5)) |>
  parameters::parameters() |>
  display()
```

```{r}
anova(
  lavaan::cfa(m7, data = data6), 
  lavaan::cfa(m7h1, data = data6), 
  lavaan::cfa(m7h3, data = data6)) |>
  parameters::parameters() |>
  display()
```

None of the model can be properly estimated (variances are negative).
